Draft1

### 2014-12-11 PresentationandPaper/Draft1.Rmd
Added text about data selection and sources and started histogram

---
title: "Draft1"
author: "Sam"
date: "December 11, 2014"
output: html_document
---

#### Quantitative Analysis of the Impact of Education on Entrepreneurship

**Data Sources**  
To complete a quantitative analysis of the impact of educational factors -- specifically the encouragement of creatitivity, self-sufficiency, and personal initiative  -- on the country-level rate of entrepreneurship, we have drawn on publicly available data from the Global Entrepreneurship Monitor (GEM) National Expert Survey (NES) and Adult Population Survey (APS).

@@

After looking through the entire 2001-2010 NES data set and considering the nine entrepreneurial conditions, we decided to use this data set to

@@

Regarding this statement, the experts surveyed had to state whether it is:

1 completely false  
2 somewhat false  
3 neither true nor false  
4 somewhat true  
5 completely true

97 do not know  
98 not applicable

After searching through many potential data sources about education and finding no indicators suitable to trace our causal chain, we were forced to use that one item of a survey however low quality it might be.

As a matter of fact, there are many reasons for which we should be concerned about that data and its quality.

First, it was not always collected which makes any measure hard to follow through time, it is only since 2009 and 2011 that the NES was made compulsory.

Second, the National Expert Surveys are very subjective data. For each entrepreneurial framework condition, that is:

Only four experts per framework condition are consulted in each country participating.

Third, the collection of data could arguably be improved. Indeed, it is outsourced by GEM Coordination Team to national teams which seem to manage the time allowed for collection poorly ???METHODOLOGY NES REPORT HERE MAIN BIB ??? . The national teams also tend to rely solely on their own personal networks. Which does not guarantee to get the best experts on each topic.

Fourth, as a result of the flows above mentioned, we observe a lot of variation from year to year up to 0.73 on a scale from 1 to 5, that is up to 14.6% (UK 2007 / UK 2009). Which is far from what one would expect. Indeed, it seems very doubtful to say that the way of teaching in any country varies so much over time. Educational reforms are much more rare and one should on the contrary expect to see much more stability, almost a constant over a decade.

The NES at 9 entrepreneurial framework conditions (4 national experts for each)

to create graphic visualizations of participants' responses to surveys about entrepreneurship in OECD (Organisation for Economic Co-operation and Development) countries.

@@

##### Control Variables: Controlling for Classic Determinants of Entrepreneurship

To control for the general state of the economy, we included annual GDP Growth from the World Bank [World Development Indicators](http://data.worldbank.org/data-catalog/world-development-indicators) as a control variable in our regression equations.  In addition, we included a GEM indicator called "Perceived Opportunities." For each country, it is the average percentage of individuals who believe there are opportunities to start a business in their area. Since we look at average individual self-esteem in every OECD country, we believe it is appropriate to look at the opportunities perceived by the average 18-64-year-old individual in these countries.

In the future, we may revise this to include lagged GDP growth in recognition of the time taken for governments and individuals to react to the state of the economy, and are planning to include control variables from GEM. Specifically, we intend to control for the classic determinants of entrepreneurship -- economic and structural determinants. To do so, we will add the following nine key entrepreneurship conditions as defined in the GEM [National Experts Survey (NES)](http://www.gemconsortium.org/Data-Collection).

>>>>

---
title: "Draft1"
author: "Sam"
date: "December 11, 2014"
output: pdf_document
---

**Quantitative Analysis of the Impact of Education on Entrepreneurship**

*Data Sources*

To complete a quantitative analysis of the impact of educational factors -- specifically the encouragement of creatitivity, self-sufficiency, and personal initiative  -- on the country-level rate of entrepreneurship, we have drawn on publicly available data from the Global Entrepreneurship Monitor (GEM) National Expert Survey (NES) and Adult Population Survey (APS).

@@

The survey questions corresponding to these variables are as follows:

1. **Entrepreneurial Intention**: Percentage of 18-64 population (individuals involved in any stage of entrepreneurial activity excluded) who intend to start a business within three years.

2. **Nascent Entrepreneurship**: Percentage of 18-64 population who are currently a nascent entrepreneur, i.e., actively involved in setting up a business they will own or co-own; this business has not paid salaries, wages, or any other payments to the owners for more than three months.

3. **Established Entrepreneur**: Percentage of 18-64 population who are currently owner-manager of an established business, i.e., owning and managing a running business that has paid salaries, wages, or any other payments to the owners for more than 42 months.

4. **Way of Teaching**: In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative.

5. **Perceived Capabilities**: Percentage of 18-64 population who believe to have the required skills and knowledge to start a business

6. **Fear of Failure**: Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business.

7. **Perceived Opportunities**: Percentage of 18-64 population who see good opportunities to start a firm in the area where they live

The APS data represent the national-level average of values between 1 and 100 that were gathered as responses to surveys within each country.  The NES data is calculated based on the average answer to a survey to the national experts.  For each question, the experts surveyed had to state whether it is:

1. Completely false
2. Somewhat false
3. Neither true or false
4. Somewhat true
5. Completely true

(97. Do not know)  
(98. Not applicable)

**Analytical Framework**

To examine the specific effect of the Way of Teaching on the rate of entrepreneurship we decided to select the following dependent, control, and explanatory variables.

Variable | Indicator 
-------------|---------------
Y Dependent Variable | Rate of Entrepreneurship (Intention, Nascent, Established)
X1 Explanatory Variable | Way of Teaching
X2 Control Variable | Perceived Capabilities
X3 Control Variable | Fear of Failure / Perceived Opportunities
X4 Control Variable | Perceived Opportunities

..........(Describe why we use the rate of entrepreneurship indicators we chose)

As a reference, we can show the distribution of our explanatory variable "Way of Teaching" in the following histogram.

```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}

# Set working directory
setwd('~/Assign2Education/PresentationandPaper')

# Library required packages
library(ggvis)
library(devtools)
library(googleVis)
library(countrycode)
library(repmis)
library(reshape2)
library(shiny)
library(httpuv)

# Create a vector of packages used
pkgs <- c('repmis', 'ggvis', 'devtools', 'googleVis', 'countrycode', 'reshape2', 'shiny', 'httpuv', 'Zelig',
          'stargazer', 'Amelia')

# Create citations txt file
repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')

# Import WayofTeaching data
wot <- repmis::source_data()

ggvis(wot, props(x= ))

ggvis(faithful, props(x = ~eruptions, fill := "#fff8dc")) +
  layer_histogram(binwidth = 0.25) +
  guide_axis("x", title = "eruptions") +
  guide_axis("y", title = "count")

```

@@

@@
